\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.5cm,right=9.5cm,marginparwidth=7.5cm,marginparsep=0.75cm,top=0.75cm,bottom=0.75cm}

\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi


% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% -------------------------------------------------
%%      PERSONAL DETAILS
%% -------------------------------------------------

\begin{document}
\name{Dhruv Upadhyay}
\tagline{Computer Science Student}

%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{dhruv.upadhyay@nextech.io}
  \phone{+91 7016400304}
%  \mailaddress{Address, Street, 00000 County}
  \location{Chennai, India}
%  \twitter{@zackbare1}
  \linkedin{linkedin.com/in/intmanear/}
   \github{github.com/intmanear}
   \par
   \email{dhruvu@acm.org}
}
%%\personalinfo{\email{dhruvu@acm.org}}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% -------------------------------------------------
%%      EDUCATION
%% -------------------------------------------------

\cvsection[sidebar]{Education}
\cvevent{Computer Science and Engineering}{SRM Institute of Science and Technology, GPA: 9.60}{2018 -- Present}{Chennai,India}
B.Tech in Computer Science and Engineering with specialization in Big Data Analytics.

%\divider
\dotfill

\cvevent{Senior Secondary Education}{The Aditya Birla Public School}{2016-18}{Bharuch,Gujarat,India}
%Central Board of Secondary Education
%\divider

\cvevent{Secondary Education}{The Aditya Birla Public School}{2013-16}{Bharuch,Gujarat,India}
%% -------------------------------------------------
%%      CO-CURRICULAR/ EVENTS
%% -------------------------------------------------
\begin{comment}
\cvsection{Co-curricular/ Events}
\smallskip
\large{\textbf{SRM Annual Research Day 2019}}
\begin{itemize}
\item[\faTrophy] Participated in 'SRM Research Day 2019', held on 26th February 2019 held by SRM IST and successfully bagged Silver Medal for Research Paper in Computer Science and Engineering Department.
\end{itemize}
\smallskip
\large{\textbf{HSC Merit Scholarship}}
\begin{itemize}
\item[\faTrophy] Scored more than 90\% in PCM (Physics, Chemistry, Maths) in 12th board examinations and got selected for the scholarship program by SRM wherein the students are given concessions on the college tution fees.
\end{itemize}
\smallskip
\large{\textbf{Rotary Interact Member 2017-18}}
\begin{itemize}
\item[\faTrophy]Organized projects all round the year that helped our school and community and that promoted international understanding. Held the post of Project Director for various successful projects that spanned from visiting Old-Age homes to interacting with children at special needs schools.

Took part in Rotary Youth Leadership program. Helped organize events and interacted with numerous luminaries.
\end{itemize}
\smallskip
\large{\textbf{National Cyber Olympiad 2018 and National Science Olympiad 2018}}
\begin{itemize}
\item[\faTrophy]Secured a world rank of 71 in National Cyber Olympiad 2018. 

Got selected for the Round 2 in NSO after clearing Problem Solving and Science Questionnaire stage, held by Science Olympiad Foundation.\\
\end{itemize}
\smallskip
\end{comment}
%% -------------------------------------------------
%%      Experience
%% -------------------------------------------------

\cvsection{Experience}
\cvevent{\textbf{Head \& AI Researcher}}{McCarthy (AI) Lab, Next Tech Lab}{July 2019-present}{Chennai, India}
\begin{itemize}
    \item [$\bullet$]Understanding and implementing various Machine Learning and Deep Learning Algorithms and Undertake various individual and collaborative projects.
    %\item [$\bullet$]Introduce revised policies to inculcate a productive environment at the lab.
    \item [$\bullet$]Mentoring the new recruits and current members of the lab in the field and introducing revised policies to inculcate a productive environment at the lab.
\end{itemize}
\cvevent{\textbf{Intern Contractor}}{ChainAim Technologies}{February 2020-present}{Distance}
\begin{itemize}
    \item [$\bullet$]Working as an AI developer and Blockchain consultant.
    %\item [$\bullet$]Introduce revised policies to inculcate a productive environment at the lab.
    \item [$\bullet$]Exploring and finding new \& innovative solutions for industrial use.
\end{itemize}
\cvevent{\textbf{Chairman}}{ACM Student Chapter, SRM}{August 2019-present}{Chennai, India}
\begin{itemize}
    \item [$\bullet$]Analyze operations to evaluate performance of the chapter and its staff in meeting objectives.
    \item [$\bullet$]Conduct and participate in inter-chapter and intra-chapter meetings.
    %\item [$\bullet$]
\end{itemize}
\cvevent{\textbf{Campus Ambassador}}{Zubi.io}{September 2019-present}{Chennai, India}
\begin{itemize}
    \item [$\bullet$]Handling the student outreach program by Zubi.io .
    \item [$\bullet$]Conducting and organizing events to spread the knowledge of\\* Blockchains among students.
    \item [$\bullet$]Promoting the use of blockchains in student-undertaken projects.
    %\item [$\bullet$]
\end{itemize}
%\begin{itemize}
%\item [$\bullet$]\large{\textbf{\cvevent{Head & Mentor}}}
%\end{itemize}

%\divider
%% -------------------------------------------------
%%      Achievements
%% -------------------------------------------------
\cvsection{Achievements}
\smallskip
\large{\textbf{Gold Medal, SRM Annual Research Day 2020}}
\begin{itemize}
\item[\faTrophy]\begin{comment} Participated in 'SRM Research Day 2019', held on 28th February 2020 held by SRM IST and \end{comment}
Successfully bagged \textbf{Gold Medal} for Research Paper on 'SRM Research Day 2020'
\end{itemize}
\smallskip
\large{\textbf{Silver Medal, SRM Annual Research Day 2019}}
\begin{itemize}
\item[\faTrophy]\begin{comment} Participated in 'SRM Research Day 2019', held on 26th February 2019 held by SRM IST and \end{comment}
Successfully bagged \textbf{Silver Medal} for Research Paper on 'SRM Research Day 2019'
\end{itemize}
\smallskip
\large{\textbf{HSC Merit Scholarship, 2018-19}}
\begin{itemize}
\item[\faTrophy] Scored \textbf{more than 90\% in PCM} (Physics, Chemistry, Maths) in 12th board examinations and got selected for the scholarship program.\begin{comment} by SRM wherein the students are given concessions on the college tution fees.\end{comment}
\end{itemize}
\smallskip
\begin{comment}
\large{\textbf{National Cyber Olympiad 2018}}
\begin{itemize}
\item[\faTrophy]Secured a \textbf{world rank of 71} in NCO 2018. 
\end{itemize}
\end{comment}
\begin{comment}
Got selected for the Round 2 in NSO after clearing Problem Solving and Science Questionnaire stage, held by Science Olympiad Foundation.\\
\end{comment}
\smallskip

%% -------------------------------------------------
%%      SKILLS
%% -------------------------------------------------
\begin{comment}
\cvsection{SKILLS}

\cvskill{C, C++, Windows}{5}
\divider

\cvskill{Java, \LaTeX, Linux, Word}{4}
\divider

\cvskillf{HTML, JavaScript, Mac OS,\\ PowerPoint, Excel, Photoshop}{3}
\end{comment}
%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\clearpage
\nocite{*}
\end{document}
