
%% -------------------------------------------------
%%      INTERESTS
%% -------------------------------------------------

\cvsection{Interests}
\cvtag{Problem Solving} 
\cvtag{Programming}
\cvtag{Computers}
\cvtag{Badminton}
\cvtag{Music}

%% -------------------------------------------------
%%      SKILLS
%% -------------------------------------------------

\cvsection{SKILLS}

\cvskill{Python, C++, SQL, Linux, \LaTeX, Tableau}{5}

\dotfill

\cvskill{Tensorflow, Keras, OpenAI}{}

\dotfill

\cvskill{NumPy, Pandas, MatplotLib, Scikit-learn}{3}

%% -------------------------------------------------
%%      LEARNING
%% -------------------------------------------------

\cvsection{Learning}
\begin{itemize}
    \item[--] \textbf{TensorFlow for Artificial
Intelligence, Machine Learning, and Deep
Learning, Coursera} \\Certificate ID: VR74GYDR7APR (Dec. 2019)
    \item[--] \textbf{Neural Networks and Deep Learning, Coursera} \,By Andrew Ng (May 2019)\\Certificate: coursera.org/share/2f7e2c89e1754939123283808465852c
    \item[--] \textbf{Reinforcement Learning, Youtube} \,By David Silver
\end{itemize}


%% -------------------------------------------------
%%      RESEARCH WORK
%% -------------------------------------------------

\cvsection{Research Work \& Projects}

\cvproject{FlexiTest Port}
\begin{itemize}
\item Patient-centered, privacy protected testing framework leveraging blockchains/distributed data storage and zero-knowledge proof to run a point of care or home test.
%%We designed an experiment where learning agents in a virtual environment learned to play Pong with the aim of achieving expertise comparable to that of humans, with minimal training time and effort.
\end{itemize}


\cvproject{Reinforcement and Imitation learning in VirtualReality}
\begin{itemize}
\item Proposal of a novel learning mechanism which combines Reinforcement learning and Imitation learning, and explores the trade-off in performance between the two approaches. Thus, achieving expertise comparable to that of humans, with minimal training time and effort.
%%We designed an experiment where learning agents in a virtual environment learned to play Pong with the aim of achieving expertise comparable to that of humans, with minimal training time and effort.
\end{itemize}
\cvproject{Intracranial hemorrhage detection using Neural Networks}
\begin{itemize}
\item https://arxiv.org/abs/2005.08644 
%%\\The The process of reviewing medical images of the patient’s cranium to look for the presence, location and type of hemorrhage is complicated and often time consuming as these scans are a combination of multiple X-Ray scans processed digitally. 
\\To reduce delays in processing of complex medical images of patient's cranium, which lead to medical complications, we propose a solution based on a Machine Vision based approach to automate the detection of intracranial hemorrhaging.  
\end{itemize}
\smallskip
\begin{comment}
\cvproject{Portable Air Conditioner (09/2015 - 12/2015)}
\begin{itemize}
\item An Innovative approach to affordable air conditioning for user who cannot afford an A/C or the electricity costs, where the which targets the specific use of an A/C that is while sleeping, by cooling only the bed and its surroundings. A prototype for which was also made. Presented at CBSE Science Exhibition, state level on 17-19 Dec 2015.
\end{itemize}
\end{comment}
%% -------------------------------------------------
%%      CAREER INTERESTS
%% -------------------------------------------------

\cvsection{Career Interests}
\cvtag{Data Science}
%%\cvtag{Reinforcement Learning}
\cvtag{Finance/ Fintech} \cvtag{Big Data}
%\cvtag{}
\cvtag{Leadership/Management}
%%\cvtag{Software}
\cvtag{Business Analysis}


\cvsection{Co-curricular/ Events}
\large{\textbf{Rotary Interact Member 2017-18}}
\begin{itemize}
\item[\faTrophy]Organized projects all round the year that helped our school and community. Was part of successful projects that spanned from visiting Old-Age homes to interacting with children at special needs schools. Took part in \textbf{Rotary Youth Leadership program} and interacted with numerous luminaries.
\end{itemize}
